Glyph-maps for Visually Exploring Temporal Patterns in Climate Data and Models

### 2012-05-15 revision-final/paper.tex
fixed Kelvin refs

To observe the scale of the measurements represented by the glyphs secondary legend plot is generated and displayed alongside the glyph-map, of all the glyphs overplotted, with complete axes. See, for example, Figure \ref{fig:nasa-glyph} where from the legend it can be seen that months range from 0 to 72 and de-seasonalized temperature ranges from -8 to 8$^0$K. In Figure \ref{fig:ref-basic}, months range from 1 to 12, and temperature from 270 to 315$^o$K.

>>>>

To observe the scale of the measurements represented by the glyphs, a secondary legend plot of all the glyphs overplotted, with complete axes is generated, and displayed alongside the glyph-map. See, for example, Figure \ref{fig:nasa-glyph} where from the legend it can be seen that months range from 0 to 72 and de-seasonalized temperature ranges from -8 to 8 K. In Figure \ref{fig:ref-basic}, months range from 1 to 12, and temperature from 270 to 315 K.
